\textbf{Manual Coding Handbook} \\[1cm] A New Indicator of Automation \\ Based on Patent Text Search

### 2015-05-19 manual_classification/manual_coding_handbook.tex
Work on manual coding
Add version number when drawing patents for manual classification and include new example (Van Halen Guitar Patent)

\definecolor{mygrey}{rgb}{0.85,0.85,0.85} % make grey for the table
\definecolor{mytextgrey}{rgb}{0.25, 0.25, 0.25} % make grey for text
% --------------------------------------------------------

@@

	\begin{itemize}	
	\item An \textit{automat} is a \textbf{device}$^1$ that carries out a \textbf{process}$^2$ \textbf{independently}$^3$.
		\begin{itemize}	
		\item $^1$: could be a physical machine, computer program, a robot.
		\item $^2$: could be a production process, the act of creation, composing a song, altering something, measuring something, a task
		\item $^3$: without human interference (apart from that needed for supervision, maintenance or at the start)
		\end{itemize}
		\item What we are not looking for: 
			\begin{itemize}
			\item tools, labor efficiency-enhancing machines
			\item business or production methods and techniques
			\item new chemicals or medical drugs
			\end{itemize}			
	\end{itemize}
\vspace{0.6cm}
\textcolor{beamer@blendedblue}{\textbf{Our question to you:}}
	\begin{itemize}	
	\item Does the patent we will show you, \textit{even just in a loose sense}, describe an automat?
	\end{itemize}
\end{frame}

@@

\begin{frame}\frametitle{Example: automation patent (a clear case)}
\href{https://www.google.de/patents/US5531156?dq=5531156&hl=en&sa=X&ei=KPtRVd3vHYOssgGe2YGQDg&ved=0CCAQ6AEwAA}{\texttt{5531156: Automatic taco machine}}
	\begin{itemize}	
	\item We classify this as an automation patent as it automates the process of cooking tacos, keeping them fresh and filling them with minimal human input or interaction. 
	\item We classify this as not a cognitive, but as a manual automation patent.
	\end{itemize}
\end{frame}

\begin{frame}\frametitle{Example: automation patent (a clear case)}
\href{https://www.google.de/patents/US6362849?dq=6362849&hl=en&sa=X&ei=k-9RVZjJHMmcsgHbvYCIDA&ved=0CCAQ6AEwAA}{\texttt{6362849: Color measuring method and device }}
	\begin{itemize}	
	\item This patent contains a video camera, a processor and the program to measure color. We classify this as an automation patent as it works independently of carrying out the process of recognizing colors.
	\item We classify this as both a cognitive and a manual automation patent.
	\end{itemize}
\end{frame}

\begin{frame}\frametitle{Example: automation patent (a borderline case)}
\href{https://www.google.de/patents/US8497785?dq=8497785&hl=en&sa=X&ei=2O5RVYD3L4GWsAGt0oCgCA&ved=0CCEQ6AEwAA}{\texttt{8497785: Handheld electronic device and method for disambiguation of text input providing suppression of low probability artificial variants}}
	\begin{itemize}	
	\item We classify as an automation patent, as it automates the process of recognizing complete words that are likely to occur from only a few letters that are entered.
	\item What makes this a boarderline case is that it is close to being a tool that is used interactively by people.
	\item As the patent contains both a small machine and the software to it with we classify this as both a cognitive and a manual automation patent
	\end{itemize}
\end{frame}

\begin{frame}\frametitle{Example: automation patent (a borderline case)}
\href{https://www.google.de/patents/US6905407?dq=6905407&hl=en&sa=X&ei=XfJRVYDIAYmosAGKx4CwCw&ved=0CCEQ6AEwAA}{\texttt{6905407: Gaming device having display with interacting multiple rotating members and indicator}}
	\begin{itemize}	
	\item This is an automation patent as it automates the process of dealing hands for ``including but not limited to the games of slot, poker, keno, blackjack, bunco and checkers". What makes this a borderline case is the high degree of human interaction with the machine. Nevertheless, once the machine has been installed, it operates independently and with a high degree of sophistication.
	\item It contains both the physical machine (which also has moving parts) and the software (like programs to play games with) to run on it, so we classify it as both cognitive and manual.
	\end{itemize}
\end{frame}

\begin{frame}\frametitle{Example:  \textbf{not} automation patent (a borderline case)}
\href{https://www.google.de/patents/US8457498?dq=8457498&hl=en&sa=X&ei=BgRSVYnsIMmdsgG_tYHQDQ&ved=0CCAQ6AEwAA}{\texttt{8457498: Methods and apparatus for target identification}}
	\begin{itemize}	
	\item This patent is a system to differentiate enemy and friendly troops through a system of back and forth communication. 
	\item We classify this as not an automation patent, but it's a close call. The process automates the identification of enemy targets. However, it does so in a large scale back and forth communication manner that more resembles a business operation process. This is not what we understand as an automat.
	\end{itemize}
\end{frame}

\begin{frame}\frametitle{Example: \textbf{not} automation patent (a borderline case)}
\href{https://www.google.de/patents/US5505821?dq=5505821&hl=en&sa=X&ei=DvRRVbmqEomrsAHtxIE4&ved=0CCEQ6AEwAA}{\texttt{5505821: Turbulence insert of a papermaking machine}}
	\begin{itemize}	
	\item This is part of a machine which automates the process of paper making. However, it is only a small part of it related to the flow of materials.
	\end{itemize}
\end{frame}

\begin{frame}\frametitle{Example: \textbf{not} automation patent (a clear case)}
\href{https://www.google.de/patents/US5552597?dq=5552597&hl=en&sa=X&ei=mvtRVYXNNomjsAHFi4GYBw&ved=0CCEQ6AEwAA}{\texttt{5552597: Hand-held scanner having adjustable light path }}
	\begin{itemize}	
	\item This is a small hand-held version of a larger desktop scanner which delivers an electronic version of printed text. 
	\end{itemize}
\end{frame}

\begin{frame}\frametitle{Example: \textbf{not} automation patent (a clear case)}
\href{https://www.google.de/patents/US7878521?dq=7878521&hl=en&sa=X&ei=VfZRVe_QMsGzswHZtYHwDA&ved=0CCEQ6AEwAA}{\texttt{7878521: Bicycle frame with device cavity }}
	\begin{itemize}	
	\item This is a bicycle frame that has a cavity for sensors. It does not automate anything.
	\end{itemize}
\end{frame}

@@

>>>>

\definecolor{mygrey}{rgb}{0.85,0.85,0.85} % make grey for the table
\definecolor{myred}{rgb}{0.85,0.1,0.1} % make grey for the table
\definecolor{mytextgrey}{rgb}{0.25, 0.25, 0.25} % make grey for text
% --------------------------------------------------------

@@

	\begin{itemize}	
	\item An \textit{automat} is a \textbf{device}$^1$ that carries out a \textbf{process}$^2$ \textbf{independently}$^3$.
		\begin{itemize}	
		\item $^1$: could be a physical machine, computer program, a robot.
		\item $^2$: could be a production process, the act of creation, composing a song, altering something, measuring something, a task
		\item $^3$: without human interference (apart from that needed for supervision, maintenance or at the start)
		\end{itemize}
		\item What we are not looking for: 
			\begin{itemize}
			\item tools, labor efficiency-enhancing machines
			\item business or production methods and techniques
			\item new chemicals or medical drugs
			\item parts of computers or of sofware that does not directly contribute to automation
			\end{itemize}			
	\end{itemize}
\vspace{0.6cm}
\textcolor{beamer@blendedblue}{\textbf{Our question to you:}}
	\begin{itemize}	
	\item Does the patent we will show you, \textit{even just in a loose sense}, describe an automat?
	\end{itemize}
\end{frame}

@@

\begin{frame}\frametitle{Example: automation patent (a clear case)}
\href{https://www.google.de/patents/US5531156}{\texttt{5531156: Automatic taco machine}}
	\begin{itemize}	
	\item We classify this as an automation patent as it automates the process of cooking tacos, keeping them fresh and filling them with minimal human input or interaction. 
	\item We classify this as not a cognitive, but as a manual automation patent.
	\end{itemize}
\end{frame}

\begin{frame}\frametitle{Example: automation patent (a clear case)}
\href{https://www.google.de/patents/US6362849}{\texttt{6362849: Color measuring method and device }}
	\begin{itemize}	
	\item This patent contains a video camera, a processor and the program to measure color. We classify this as an automation patent as it independently recognizes colors.
	\item We classify this as both a cognitive and a manual automation patent.
	\end{itemize}
\end{frame}

\begin{frame}\frametitle{Example: automation patent (a borderline case)}
\href{https://www.google.de/patents/US8497785}{\texttt{8497785: Handheld electronic device and method for disambiguation of text input providing suppression of low probability artificial variants}}
	\begin{itemize}	
	\item We classify as an automation patent, as it automates the process of recognizing complete words that are likely to occur from only a few letters that are entered.
	\item What makes this a boarderline case is that it is close to being a tool that is used interactively by people.
	\item As the patent contains both a small machine and the software to it with we classify this as both a cognitive and a manual automation patent
	\end{itemize}
\end{frame}

\begin{frame}\frametitle{Example: automation patent (a borderline case)}
\href{https://www.google.de/patents/US6905407}{\texttt{6905407: Gaming device having display with interacting multiple rotating members and indicator}}
	\begin{itemize}	
	\item This is an automation patent as it automates the process of dealing hands for ``including but not limited to the games of slot, poker, keno, blackjack, bunco and checkers". What makes this a borderline case is the high degree of human interaction with the machine. Nevertheless, once the machine has been installed, it operates independently and with a high degree of sophistication.
	\item It contains both the physical machine (which also has moving parts) and the software (like programs to play games with) to run on it, so we classify it as both cognitive and manual.
	\end{itemize}
\end{frame}

\begin{frame}\frametitle{Example:  \textcolor{myred}{\textbf{not}} automation patent (a borderline case)}
\href{https://www.google.de/patents/US8457498}{\texttt{8457498: Methods and apparatus for target identification}}
	\begin{itemize}	
	\item This patent is a system to differentiate enemy and friendly troops through a system of back and forth communication. 
	\item We classify this as not an automation patent, but it's a close call. The process automates the identification of enemy targets. However, it does so in a large scale back and forth communication manner that more resembles a business operation process. This is not what we understand as an automat.
	\end{itemize}
\end{frame}

\begin{frame}\frametitle{Example: \textcolor{myred}{\textbf{not}} automation patent (a borderline case)}
\href{https://www.google.de/patents/US5505821}{\texttt{5505821: Turbulence insert of a papermaking machine}}
	\begin{itemize}	
	\item This is part of a machine which automates the process of paper making. However, it is only a small part of it related to the flow of materials.
	\end{itemize}
\end{frame}

\begin{frame}\frametitle{Example: \textcolor{myred}{\textbf{not}} automation patent (a clear case)}
\href{https://www.google.de/patents/US5552597}{\texttt{5552597: Hand-held scanner having adjustable light path }}
	\begin{itemize}	
	\item This is a small hand-held version of a larger desktop scanner which delivers an electronic version of printed text. 
	\end{itemize}
\end{frame}

\begin{frame}\frametitle{Example: \textcolor{myred}{\textbf{not}} automation patent (a clear case)}
\href{https://www.google.de/patents/US7878521}{\texttt{7878521: Bicycle frame with device cavity }}
	\begin{itemize}	
	\item This is a bicycle frame that has a cavity for sensors. It does not automate anything.
	\end{itemize}
\end{frame}

\begin{frame}\frametitle{Example: \textcolor{myred}{\textbf{not}} automation patent (a clear case)}
\href{http://www.google.com/patents/US4656917}{\texttt{4656917: Musical instrument support }}
	\begin{itemize}	
	\item This patent by the guitarist Van Halen describes a device that allows for more creative guitar handling and playing. It does not automate anything, but rather enables a person to do something she could not previously do.
	\end{itemize}
\end{frame}

@@

\begin{frame}\frametitle{FAQs}
	\begin{itemize}	
	\item \textit{Can I enter something else like 1? if I'm not quite sure?}\\[0.1cm]
	No, please write your remarks in the comment box if you're not sure. 
	\end{itemize}
\end{frame}
